---
title: DANL Project
subtitle: "Data-Driven Mastery: Unlocking Business Potential"
author: 
  - Name Jack Helrigel
  - Name Owen Ellick
  - Name Luca Schettino
  - Name Jake Starkey

toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

from: markdown+emoji
---
```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```



# Introduction

About this project 👏 Welcome to our Project, where we dive into the dynamic world of professional basketball through the lens of players salaries and performance statistics. We will analyzing a dataset with NBA Players Salaries and statistics from the 2022-2023 NBA season.

```{r}
library(tidyverse)
library(skimr)
```


# Data

The data.frame `NBAsal` contains a data from the 2022-2023 NBA season. It contains player per-game and advanced statistics for that season with player salary data. This allows us to create a comprehensive resource for understanding the performance and financial aspects of professional basketball players.

## Summary Statistics

```{r}
NBAsal <-read_csv("nba_salaries.csv")
```
```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(NBAsal)
```


```{r}
skim(NBAsal) %>% 
  select(-n_missing)
```


```{r}

```


## MPG and a Type of Cars
The following boxplot shows how the distribution of highway MPG (`hwy`) varies by a type of cars (`class`) :blue_car: :truck: :minibus:.


```{r}
ggplot(data = mpg) +
  geom_boxplot(aes(x = class, y = hwy, fill = class),
               show.legend = F) +
  labs(x = "Class", y = "Highway\nMPG") 
```


